Points Above Replacement

### 2022-04-27 Code/NBAPARCode.Rmd
use relative path in code for portability

```{r data, include=FALSE}
league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
```

>>>>

```{r data, include=FALSE}
## use relative path for portability
league <- read.csv(file = '../Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
```
